---
title: "10-import"
output: html_notebook
---
## Load needed libraries and dataset
```{r load dataset and library}
# import dataset and library
library(tidyverse)
library(stringr)
library(dplyr)
library(assertr)
library(readr)
library(janitor)
Hostel <- read_csv("Hostel.csv")
```


## Describe the data
The dataset I choose is Japan Hostel Dataset, which has 342 hostels in Japan. It includes 16 columns:
hostel number: hostel's number
hostel.name: name of hostel
City: location of hostel
price.from: price of hostel
Distance: distance from hostel to city centre
summary.score: overall score of hostel which equals to the average of the following 8 columns
rating.band: rating band of hostel, which includes "Superb", "Fabulous", "Very Good", "Good" and "Rating"
atmosphere: rating of atmosphere in hostel
cleanliness: rating of cleanliness of hostel
facilities: quality of hostel's facilities
location.y: rating of hostel's location
security: rating of surrounding and hostel security
staff: rating of staff
valueformoney: whether it is worthwhile to choose the hostel
lon: longitude of hostel
lat: latitude of hostel


## Read in and check data
Brief view of data
```{r brief view of data}
# show first 6 rows of data 
head(Hostel)
```


Detect the attribute of each column
```{r check data}
str(Hostel)
```


Detect whether there is any null or NA value in dataset
```{r detect null and NA value}
# detect null value
is.null(Hostel)

# detect NA value
Hostel %>% 
  verify(!is.na(.))
```
Therefore the dataset has 0 null value and 223 NA values.


Check extreme value in 8 rating columns
```{r check extreme value in 8 rating columns}
Hostel%>%
  assert(within_bounds(0,10),summary.score)%>% # check if there exist extreme value in summary.score
  assert(within_bounds(0,10),atmosphere)%>% # check if there exist extreme value in atmosphere
  assert(within_bounds(0,10),cleanliness)%>% # check if there exist extreme value in cleanliness
  assert(within_bounds(0,10),facilities)%>% # check if there exist extreme value in facilities
  assert(within_bounds(0,10),location.y)%>% # check if there exist extreme value in location.y
  assert(within_bounds(0,10),security)%>% # check if there exist extreme value in security
  assert(within_bounds(0,10),staff)%>% # check if there exist extreme value in staff
  assert(within_bounds(0,10),valueformoney) # check if there exist extreme value in valueformoney
```
The result shows that there are not any extreme value in 8 rating columns.


## Clean up the data. 
In last chunk, we knew that the dataset has already recorded NA values. Therefore we do not need to do it again. In this section, I want to make the column Distance into a column which only contains numbers, because numeric data is easier to be analysed. So I delete the words in Distance.    
```{r data cleaning}
# remove certain words from Distance 
for(i in 1:nrow(Hostel)){
  Hostel$Distance[i] <- gsub("km from city centre","",Hostel$Distance[i])
}

# change Distance's type into numeric
Hostel$Distance <- as.numeric(Hostel$Distance)
# check the result
str(Hostel)
```
Now the column Distance has been successfully changed into numeric column.

